---
title: "Testing General Blastula Emails"
author: "Noam Ross"
date: "4/9/2021"
output: html_document
params:
  recipients:
    - ross@ecohealthalliance.org
    - young@ecohealthalliance.org
    - noam.ross@gmail.com
---

_For a more elaborate working example, see <https://connect.eha.io/content/37> (EHA-Connect account required)_

This R Markdown document tests sending blastula emails to arbitrary users, with and without EHA RStudio Connect credentials. It can be used to send scheduled messages, for instance.

```{r setup, include=FALSE}
library(blastula)
library(rmarkdown)
knitr::opts_chunk$set(echo = TRUE)
```

We store the *app password* for the email account sending the variables as an environment variable on RStudio Connect as `"SMTP_PASSWORD"`, and use it to make credentials:

```{r}
email_creds <- creds_envvar(
  user = "rsconnect@ecohealthalliance.org",  # Account that has the app pwd
  #  pass_envvar = "SMTP_PASSWORD",           # Commenting out to show this is the default, not needed
  host = "smtp.gmail.com",                   # Our email provider, do not change
  port = 587,                                # The appropriate port, do not change
  use_ssl = TRUE                           # SSL required or emails don't send, do not change
)
```

Now I create an email message from another R Markdown file.

```{r}
email_body <- render_email("blastula-email.Rmd")
```

We send this to the recipients in the Rmd header, who are:

```{r results='asis'}
cat(paste('-', params$recipients), sep = '\n')
```

```{r}
smtp_send(
  email_body,
  from = "rsconnect@ecohealthalliance.org",    # Should match the email used to make the credentials
  to = params$recipients,                  # Recipients set in the document header
  subject = "A test email from RStudio Connect",
  credentials = email_creds        # Credentials we made using the env var
)
```
